Parsing Postfix log files

### 2008-04-29 doc/logparser-other-parsers-review.tex
Tested Isoqlog and Anteater. Didn't test "Log analyser --- throughput monitor" - it would be pointless.

Isoqlog produces a report listing the number of mails sent by each unique
sender address, and separately the total number of bytes transferred; both
reports are produced for daily, monthly and annual time spans, but only for
the domains listed in its configuration file (making it impossible to
produce reports for every sender domain).  It appears to ignore all log
lines except for those for the current day, though it does maintain a
record of data previously extracted, which the newly extracted data is
merged into (no information is provided on the format of the data store).
The data extracted appears to be limited to the number of mails sent by
each sender, unlike the copious amounts of data extracted by \parsername{}.
It doesn't utilise rejection log lines in any way, so is unsuitable for the
purposes of this project.  Its parsing is completely inextensible, indeed
is almost incomprehensible, relying on \texttt{scanf(3)}, fixed offsets and
low level string manipulation; it is the opposite end of the spectrum to
\parsernames{} parsing.  It doesn't handle any of the complications
discussed in this document, doesn't gather the breadth of data required for
this project, and ignores the majority of log lines produced by Postfix.

@@

>>>>

Isoqlog produces a report listing the number of mails sent by each unique
sender address, and separately the total number of bytes transferred; both
reports are produced for daily, monthly and annual time spans, but only for
the domains listed in its configuration file (making it impossible to
produce reports for every sender domain).  It appears to ignore all log
lines except for those for the current day, though it does maintain a
record of data previously extracted, which the newly extracted data is
merged into (no information is provided on the format of the data store).
The data extracted appears to be limited to the number of mails sent by
each sender, unlike the copious amounts of data extracted by \parsername{}.
It doesn't utilise rejection log lines in any way, so is unsuitable for the
purposes of this project.  Its parsing is completely inextensible, indeed
is almost incomprehensible, relying on \texttt{scanf(3)}, fixed offsets and
low level string manipulation; it is the opposite end of the spectrum to
\parsernames{} parsing.  It doesn't handle any of the complications
discussed in this document, doesn't gather the breadth of data required for
this project, and ignores the majority of log lines produced by Postfix.
It ignores all log lines earlier than today, so testing with the test log
files is pointless.

@@

The Debian project (\url{http://www.debian.org/}) provides a manual page
with the copy of anteater it distributes, so the author was at least able
to run anteater with the correct arguments; sadly anteater produced zero
for every statistic, presumably because it was unsuccessful in parsing the
log lines.
